\documentclass[a4paper,oneside,11pt]{report}

\usepackage{mystyle}
\begin{document}
\pagenumbering{Alph}
\pagestyle{empty}
\input{./tex/frontpages}
\pagestyle{plain}
\clearpage\pagenumbering{Roman}
\addcontentsline{toc}{section}{Abstract}
\input{./tex/abstract}
\clearpage
\addcontentsline{toc}{section}{Acknowledgement}
\input{./tex/acknowledgements}
\clearpage
\addcontentsline{toc}{section}{Dedication}
\input{./tex/dedication}
\clearpage

\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents
\clearpage
\addcontentsline{toc}{section}{\listtablename}
\listoftables
\clearpage
\addcontentsline{toc}{section}{\listfigurename}
\listoffigures
\clearpage\pagenumbering{arabic}
\input{./tex/introduction} %includes background
\input{./tex/motivation}
\input{./tex/background_study} % includes intro of liturature review

\input{./tex/Methodology}
\input{./tex/tf}
\input{./tex/gnb}
\input{./tex/svm}
\input{./tex/li_r}
\input{./tex/lo_r}
\input{./tex/nn}
\input{./tex/d_s}
\input{./tex/d_c}
\input{./tex/d_f}
\input{./tex/e_r}
\input{./tex/e}
\input{./tex/e_r_gnb}
\input{./tex/e_r_svm}
\input{./tex/e_r_lir}
\input{./tex/e_r_lor}
\input{./tex/e_r_nn}
\input{./tex/comparison}
\input{./tex/dicussion}
\input{./tex/conclusion}
\input{./tex/future_work}
\clearpage
\renewcommand\bibname{References}
\bibliographystyle{IEEEtran}
%\bibliography{IEEEabrv,4_2_refs}


\begin{thebibliography}{9}

\bibitem{latexcompanion} 
B. F. Marko Tkalcic and M. Schedl. 
\textit{Personality traits and the relationship with (non-) disclosure behavior on Facebook}. 
Proceedings of the 25th International Conference Companion on World Wide Web, pp. 565–568, 2016. [Online]. Available: 
\\\texttt{http://dl.acm.org/citation.cfm?id=2890085}

\bibitem{latexcompanion} 
L. S. Alan Menk. 
\textit{Predicting the human curiosity from users profiles on Facebook}. 
Proceedings of the 4th Spanish Conference on Information Retrieval Article No. 13, 2016. [Online]. Available: 
\\\texttt{http://dl.acm.org/citation.cfm?id=2934743}

\bibitem{latexcompanion} 
T. G. P. K. Yoram Bachrach, Michal Kosinski and D. Stillwell.
\textit{Personality and patterns of Facebook usage}. 
Proceedings of the 4th Annual ACM Web Science Conference, pp. 24–32, 2012. [Online]. Available:
\\\texttt{http://dl.acm.org/citation.cfm?id=2380722}

\bibitem{latexcompanion} 
A. C. Reza Farahbakhsh, Xiao Han and N. Crespi. 
\textit{Analysis of publicly disclosed information in Facebook profiles}. 
Advances in Social Networks Analysis and Mining (ASONAM), 2013 IEEE/ACM International Conference, 2013. [Online]. Available:
\\\texttt{http://ieeexplore.ieee.org/document/6785779/}

\bibitem{latexcompanion} 
S. P. Thomas Theodoridis and Y. Kompatsiaris. 
\textit{Assessing the reliability of Facebook user profiling}. 
Proceedings of the 24th International Conference on World Wide Web, pp. 129–130, 2015. [Online]. Available:
\\\texttt{http://dl.acm.org/citation.cfm?id=2742728}

\bibitem{latexcompanion} 
Zhenhui Li, Ding Zhou, Yun-Fang Juan and Jiawei Han. 
\textit{Keyword Extraction for Social Snippets}. 
Proceedings of the 19th international conference on World wide web, pp. 1143-1144 , 2010. [Online]. Available:
\\\texttt{http://dl.acm.org/citation.cfm?id=1772845}

\bibitem{latexcompanion} 
Aparna Garimella and Rada Mihalcea. 
\textit{Zooming in on Gender Differences in Social Media}. 
2016. [Online]. Available:
\\\texttt{https://www.semanticscholar.org/paper/Zooming-in-on-Gender-Differences-in-Social-Media-Garimella-Mihalcea/753d714f9efe23ebb7996f276a10fe233c1ca741}

\bibitem{latexcompanion} 
Jennifer Golbeck, Cristina Robles and Karen Turner.
\textit{Predicting Personality with Social Media}. 
CHI '11 Extended Abstracts on Human Factors in Computing Systems, pp. 253-262, 2011. [Online]. Available:
\\\texttt{https://www.semanticscholar.org/paper/Zooming-in-on-Gender-Differences-in-Social-Media-Garimella-Mihalcea/753d714f9efe23ebb7996f276a10fe233c1ca741}

\bibitem{latexcompanion} 
Yin Zhu, Erheng Zhong, Sinno Jialin Pan, Xiao Wang, Minzhe Zhou and Jiawei Han. 
\textit{Predicting user activity level in social networks}. 
Proceedings of the 22nd ACM international conference on Information & Knowledge Management, pp. 159-16, 2013. [Online]. Available:
\\\texttt{http://dl.acm.org/citation.cfm?id=2505518}

\bibitem{latexcompanion} 
Jalal S. Alowibdi, Ugo A. Buy and Philip Yu. 
\textit{Language Independent Gender Classification on Twitter}. 
Proceedings of the 2013 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining, pp. 739-743, 2013. [Online]. Available:
\\\texttt{http://dl.acm.org/citation.cfm?id=2492632&CFID=983309617&CFTOKEN=98982289}

\end{thebibliography}


%\begin{appendices}
	% \input{./tex/commands}
%\end{appendices}
\end{document}